Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-12-11 text/supp.tex
Remove a comment in a Stan model

\section{Data selection}

@@

\section{Details on the heavy-tailed Gompertz probability model}

@@

\section{Alternative priors}

@@

\section{Alternative population models}

@@

\subsection{Autocorrelated residuals}

@@

\subsection{Assumed density independence}\label{assumed-density-independence}

@@

\subsection{Assumed observation error}

@@

\subsection{Ricker-logistic}

@@

\section{Simulation testing the model}

@@

\subsection{Estimating $\nu$ from a stationary t distribution}

@@

\subsection{Heavy-tailed Gompertz model simulations}

@@

\section{Modelling covariates of heavy-tailed dynamics}

@@

\section{Additional acknowledgements}

@@

\renewcommand{\baselinestretch}{\tighttextstretch}
\normalsize
\bibliographystyle{apalike}
\bibliography{/Users/seananderson/Dropbox/tex/jshort,/Users/seananderson/Dropbox/tex/ref3}
\renewcommand{\baselinestretch}{\textstretch}
\normalsize

% ------------------------------
% Supplemental Tables
% ------------------------------

@@

\renewcommand{\baselinestretch}{\tighttextstretch}
\normalsize
\begin{footnotesize}
\noindent
{\tt
\input{../analysis/mainids}
}
\end{footnotesize}
\renewcommand{\baselinestretch}{\textstretch}
\normalsize
%\end{spacing}

>>>>

\subsection{Data selection}

@@

\subsection{Details on the heavy-tailed Gompertz probability model}

@@

\subsection{Alternative priors}

@@

\subsection{Alternative population models}

@@

\subsubsection{Autocorrelated residuals}

@@

\subsubsection{Assumed density independence}\label{assumed-density-independence}

@@

\subsubsection{Assumed observation error}

@@

\subsubsection{Ricker-logistic}

@@

\subsection{Simulation testing the model}

@@

\subsubsection{Estimating $\nu$ from a stationary t distribution}

@@

\subsubsection{Heavy-tailed Gompertz model simulations}

@@

\subsection{Modelling covariates of heavy-tailed dynamics}

@@

\subsection{Additional acknowledgements}

@@

% \renewcommand{\baselinestretch}{\tighttextstretch}
% \normalsize
% \bibliographystyle{apalike}
% \bibliography{/Users/seananderson/Dropbox/tex/jshort,/Users/seananderson/Dropbox/tex/ref3}
% \renewcommand{\baselinestretch}{\textstretch}
% \normalsize
%
% ------------------------------
% Supplemental Tables
% ------------------------------

@@

\begin{scriptsize}
%\renewcommand{\baselinestretch}{1.11}
\noindent
{\tt
\input{../analysis/mainids}
}
%\renewcommand{\baselinestretch}{\textstretch}
\end{scriptsize}
\normalsize
%\end{spacing}
